Timbral similarity between extended playing techniques: the next frontier in querying instrumental databases

### 2018-01-28 paper/lagrangeSpontaneousSimilarity2017.tex
bis
comment on Dendrogram

\section*{Acknowlegments}

The authors would like to thank PSL for funding this research, CNSMDP for fruitful collaboration and Ircam for providing access to the SOL database.

@@

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% ACKNOWLEDGMENTS %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Acknowlegments}

The authors would like to thank
PSL for funding this research,
CNSMDP for fruitful collaboration,
and Ircam for providing access to the SOL database.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% BIBLIOGRAPHY %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\vl{This dendrogram is very hard to read. Abbreviations must be replaced by the full names of every instrument and playing tecniques.
Another way to visualize it would be a two-dimensional embedding, such as t-SNE or Isomap (I'm biased towards Isomap). @figure
}
